---
title: "HW8"
author:
- Surafel Geleta
- ssg2775
- https://github.com/surafelgeleta/SDS_315_HW8
output:
  pdf_document: default
  html_document: default
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Calling packages
library(tidyverse)
library(mosaic)

# Reading in data
creatinine <- read.csv("C:\\Users\\gelet\\OneDrive\\Documents\\SDS315\\HW8\\creatinine.csv")
covid <- read.csv("C:\\Users\\gelet\\OneDrive\\Documents\\SDS315\\HW8\\covid.csv")
milk <- read.csv("C:\\Users\\gelet\\OneDrive\\Documents\\SDS315\\HW8\\milk.csv")
```

# Problem 1

## A

```{r echo=FALSE, message=FALSE, warning=FALSE, results = 'hide'}
# Mean creatine clearance rate grouped by age
creatinine %>% 
  group_by(age) %>% 
  summarize(mean_creatinine_clearance = mean(creatclear))
```

We should expect a creatinine clearance rate of about 114 mL/minute for a 55 year old. This was obtained by finding the mean creatinine clearance of 55 year olds in the dataset.

## Part B

```{r, echo = FALSE, message = FALSE, results = 'hide'}
# Regressing creatinine clearance rate on age
lm(creatclear ~ age, data = creatinine)
```
For every one-year increase in age, creatinine clearance should fall by -0.6198 mL/minute. I obtained this by fitting a linear model on the data, with "creatclear" as the outcome variable and "age" as the predictor, and taking the slope of the model.

## Part C

```{r echo=FALSE, results='hide', message=FALSE}
# Residual of 40-year old with 135mL/minute rate
135 - (147 - 0.6198*40)

# Residual of 60-year old with 112mL/minute rate
112 - (147 - 0.6198*60)
```
The 40-year old has a healthier creatinine clearance rate than the 60-year old. This was obtained by finding the residual for each case, which was the individual's actual creatinine clearance rate subtracted by their predicted creatinine clearance rate. The 40-year old had a residual of 12.792 mL/minute and the 60-year old had a residual of 2.188 mL/minute, indicating that the 40-year old has a higher creatinine clearance rate for his age than the 60-year old does.

# Problem 2

## 1.

```{r echo=FALSE, results='hide', message=FALSE}
set.seed(900)

# 10000 exponential models from 10000 bootstrapped samples of the data subsetted to only include Italy
boot_italy = do(10000)*lm(log(deaths) ~ days_since_first_death, data = resample(covid[covid$country == "Italy",]))

# 95% confidence interval
confint(boot_italy)

# Doubling time
70/(0.1595057*100)
70/(0.2081915*100)
```
It can be stated with 95% confidence that the true daily growth rate of COVID deaths in Italy lies between 0.159 and 0.208. It can also be stated with 95% confidence that the true doubling time of COVID deaths in Italy lies between 4.4 and 3.4 days.

## 2.

```{r echo=FALSE, results='hide', message=FALSE}
# 10000 exponential models from 10000 bootstrapped samples of the data subsetted to only include Spain
boot_spain = do(10000)*lm(log(deaths) ~ days_since_first_death, data = resample(covid[covid$country == "Spain",]))

# 95% confidence interval
confint(boot_spain)

# Doubling time
70/(0.2352879*100)
70/(0.3190304	*100)
```

It can be stated with 95% confidence that the true daily growth rate of COVID deaths in Spain lies between 0.235 and 0.317. It can also be stated with 95% confidence that the true doubling time of COVID deaths in Italy lies between 3.0 and 2.2 days.

## 3.

```{r echo=FALSE, results='hide', message=FALSE}
ggplot(covid, aes(x = days_since_first_death, y = deaths, group = country, color = country)) +
  geom_line() +
  labs(x = "Days Since First Death",
       y = "Reported Daily COVID-19 Deaths",
       title = "COVID Death Growth in Italy and Spain, Feb.-Apr. 2020")
```

# Problem 3

```{r echo = FALSE, message= FALSE, warning = FALSE, results = 'hide'}
# 10000 bootstrapped linear models regressing logarithm of sales on logarithm of milk prices 
boot_milk = do(10000)*lm(log(sales) ~ log(price), data = resample(milk))

# 95% confidence interval
confint(boot_milk)
```

Since the data follows a power law, I fit a linear model on the data and regressed the logarithm of milk sales (outcome) on the logarithm of milk prices (predictor). I repeated this 10000 times using 10000 bootstrapped samples and generated a 95% confidence interval.
From there, it can be stated with 95% confidence that the true elasticity, or percent change of milk sales when milk prices increase by 1%, lies between -1.773% and -1.458%. 
